---
title: "Comparing binary reads of OPUS with ono python package vs. opusreader in R" 
author: "Philipp Baumann, Kompetenzzentrum Boden (KOBO), Datenwissenschaften philipp.baumann@bfh.ch"
output: 
  github_document: 
    toc: yes
    toc_depth: 2 
---

# Setup to reproduce examples

-   Use [renv](https://rstudio.github.io/renv/articles/python.html) together with python virtual environments to log and restore dependencies

<!-- -->

    # install Python virtual environment in Debian
    sudo apt install python3.8-venv

Install [ono](https://pypi.org/project/ono/) via reticulate, Python virtual environments, and pip

```{bash, eval=FALSE}
sudo apt install python3-pip
pip install ono
```

```{r, eval= FALSE}
install.packages("renv")
install.packages("reticulate")
library("reticulate")
virtualenv_create("ono_opusreader")
reticulate::use_virtualenv("ono_opusreader")
virtualenv_install("ono_opusreader", "ono")
renv::use_python()
# 1: ~/.virtualenvs/ono_opusreader/bin/python
renv::snapshot()
# writes Python packages in requirements.txt
```

To deploy the R and Python environments on a new computer after cloning this repository, install python3-pip and python3.8-venv using your linux package manager (i.e. apt; see above).

```{r}
renv::restore()
# load project-local version of Python
```
